---
title: "ScriptingExercise"
author: "Naveen K Bezawada"
Student ID: "156182"
date: "8/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question


Create an R Markdown Word/HTML document which contains your information (name, etc), the question in Text form, and displays your code and the output for the below questions:


The iris dataset is 'built-in' to R-Studio like the airquality and LakeHuron datasets from HW1.

Create a character vector with length of number-of-rows-of-iris-dataset, such that, each element gets a character value – “greater than 5″ if the corresponding ‘Sepal.Length’ > 5, else it should get “lesser than 5″.


1) Make the logic for above problem statement using a 'for-loop' and a 'if-else' statement

2) Make the logic for above problem statement using a ifelse() function

3) Create a logic for the same problem statement using apply() function


      
##Soultions


      
###Soultion-1

```{r chunk_name, echo=TRUE}
x <- c()
iters=150
for (i in 1:iters){
  if (iris[i,1]> 5 ){
    x<-append(x,"greater than 5")
  }
  else 
  {
    x<-append(x,"less than 5")
  }
  
}
print (x)
```

###Solutiion-2

```{r solution2, echo=TRUE}
x<- ifelse(iris$Sepal.Length > 5, "greater than 5", "lesser than 5") 
print (x)
```

###Solution-3

```{r solution_3, echo=TRUE}

lesserThanOrGreaterThan <- function(iris){
  
  if(iris['Sepal.Length'] > 5){
    
    "greater than 5"
    
  } else {
    
    "lesser than 5"
    
  }
  
}

x <- apply(iris, 1, FUN=lesserThanOrGreaterThan)

print(x)
```

